---
title: "Model Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    source_code: embed
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(shiny)
library(dplyr)
```

```{r global, include=FALSE}

predictions <- readRDS("data/predictions.RDS") %>%
  filter(data == "test") %>%
  mutate(
    logistic_predict = ifelse(logistic_predict_no < .88, "yes", "no")
  ) %>%
  select(-c(data, logistic_predict_no))

```


# Sidebar {.sidebar}

### Inputs

```{r}

sliderInput('calls_per_day', "Calls per Day", min = 50, max = 200, value = 50, step = 50)
sliderInput('samples', "Samples", min = 100, max = 500, value = 250, step = 50)
numericInput('cost_to_market', "Cost of Call", 10)
numericInput('profit_from_sale', "Profit From Sale", 100)

```


### Filters

```{r}

sliderInput('euribor3m', "Euribor 3m", min(predictions$euribor3m), max(predictions$euribor3m), value = c(min(predictions$euribor3m), max(predictions$euribor3m)), step = .2)


```

-------

``` {r}

sliderInput('age', "Age", min(predictions$age), max(predictions$age), value = c(min(predictions$age), max(predictions$age)))
# selectizeInput('job', "Choose Jobs", choices = unique(predictions$job), selected = unique(predictions$job), multiple = TRUE)
selectizeInput('education', "Choose Education", choices = unique(predictions$education), selected = unique(predictions$education), multiple = TRUE)
checkboxGroupInput('cellphone', "Contact Method", choices = unique(predictions$contact), selected = unique(predictions$contact))

```

-------

```{r}

actionButton("go_button", "Rerun")

```

# Explanation

Using the test data from the dataset used to train the random forest model, we sample with replacement n "runs" of a fixed number of calls.  The dataset for sampling is filtered according to the parameters specified.  This sampling is repeated based on the number of inputs for the number of runs.

*Expected Value of Population Plot* 

The expected value of the population is the profit from successful sales multiplied by the number of successful calls per "run" of a specified number of calls minus the cost per those sampled (all if using the baseline model, or only those specified by the random forest model otherwise).  This is a gross value, not a per-capita value (i.e. the expected value should be about 10x greater if the number of calls per run is increased by 10x).  

*Sensitivity Vs Population Baseline (Plot)*

This plot shows the sensitivity (True Positive divided by All Positives) from the model as a function of the baseline population.  It is useful to observe whether the model performs better or worse given higher or lower baseline models.

# Plots 

## Output

### Expected Value of Population

```{r}

output$graph_two <- renderPlot({
  
  ggplot(data = samples(), mapping = aes(color = percent_overall, x = baseline_expected_value_population, y = rf_expected_value_population)) + geom_jitter() + geom_smooth() + geom_abline(intercept = 0, slope = 1)
  
})


plotOutput("graph_two")



```


## Vs Baseline

### Sensitivity vs Population Baseline

```{r}

output$graph <- renderPlot({
  
  ggplot(data = samples(), mapping = aes(x = percent_overall, y = rf_sensitivity)) + geom_boxplot(aes(group = group_for_boxplot)) + scale_x_continuous(name = "percent overall", breaks = seq(0, 1, .05)) + scale_y_continuous(name = "sensitivity", breaks = seq(0, 1, .1))
  
})


plotOutput("graph")



```

### Specificity vs Population Baseline

```{r}

output$graph3 <- renderPlot({
  
  ggplot(data = samples(), mapping = aes(x = percent_overall, y = rf_specificity)) + geom_boxplot(aes(group = group_for_boxplot)) + scale_x_continuous(name = "percent overall", breaks = seq(0, 1, .05)) + scale_y_continuous(name = "specificity", breaks = seq(0, 1, .1))
  
})


plotOutput("graph3")



```


# Raw Data

```{r}

universe_of_samples <- reactive({
  
  input$go_button
  
  to_return <- predictions %>%
    filter(
      euribor3m >= min(isolate(input$euribor3m)),
      euribor3m <= max(isolate(input$euribor3m)),
      age >= min(isolate(input$age)),
      age <= max(isolate(input$age)),
      # job %in% unique(input$job),
      education %in% unique(isolate(input$education)),
      contact %in% unique(isolate(input$cellphone))
    ) %>%
    select(term_deposit, logistic_predict, downsample_predict)


to_return

})
# --



```

```{r}

samples <- reactive({
  
  tibble(sample = (1:isolate(input$samples))) %>%
    mutate(
      data = map(sample, function(x) universe_of_samples() %>% 
                   sample_n(size = isolate(input$calls_per_day), replace = TRUE) %>%
                   summarize(
                     total_calls = nrow(.),
                     actual = sum(ifelse(term_deposit == "yes", 1, 0)),
                     random_forest = sum(ifelse(downsample_predict == "yes", 1, 0)),
                     percent_overall = round(actual / total_calls, 2),
                     rf_true_positive = round(sum(ifelse(downsample_predict == "yes" & term_deposit == "yes", 1, 0))/total_calls, 2),
                     rf_false_positive = round(sum(ifelse(downsample_predict == "no" & term_deposit == "yes", 1, 0))/total_calls, 2),
                     rf_false_negative = round(sum(ifelse(downsample_predict == "no" & term_deposit == "yes", 1, 0))/total_calls, 2),
                     rf_true_negative = 1 - rf_true_positive - rf_false_positive - rf_false_negative,
                     rf_sensitivity = (rf_true_positive/(rf_true_positive + rf_false_positive)),
                     rf_specificity = (rf_true_negative/(rf_true_negative + rf_false_negative)),
                     rf_expected_value_population = (rf_true_positive * (isolate(input$profit_from_sale) - isolate(input$cost_to_market)) + rf_false_positive * -1 * isolate(input$cost_to_market)) * random_forest,
                     baseline_expected_value_population = (percent_overall * isolate(input$profit_from_sale) +  -1 * isolate(input$cost_to_market)) * total_calls
                   )
                 )
    ) %>%
    tidyr::unnest(data) %>%
    mutate(unique_rows = nrow(universe_of_samples()),
           group_for_boxplot = .025*(round(percent_overall/.025)))
  
  
  # %>%
  #   summarize_all(function(x) str_c(quantile(x), collapse = ", "))

  
})






output$table <- renderTable({

  samples()
  
    })
  


tableOutput("table")


```
